An equivalence of compositional frameworks

### 2019-05-01 EquivCompFrameworks_20180911kc.tex
more tidying

Let $\OpFib(\A)$ denote the 2-subcategory of the slice $\mathbf{Cat}/ \A$ of opfibrations over $\A$, opfibrations morphisms and natural transformations with vertical components.

{\chris in progress}
The Grothendieck construction is a 2-functor $\int F \colon [ \mathrm{A},\mathbf{Cat}] \to \mathbf{Cat}/ \mathrm{A}$ which factors through the image of the embedding $\textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}$: $$\int F \colon [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$

{\chris edit appropriately, notation etc.}
\begin{thm}\label{thm:Grothendieck}
    \begin{enumerate}
        \item Every opfibration $\U \maps \D \to \C$ gives rise to a pseudofunctor $F_U \maps \C {\to}Cat$.
        \item Every opindexed category $F \maps \C \to Cat$ gives rise to  an opfibration $\U_F \colon \int F\to\C$.
        \item The above correspondences yield an equivalence of 2-categories 
        \begin{displaymath}
            ICat(\C) \simeq opFib(\C)
        \end{displaymath}
        so that $F_{\U_F} \cong F$ and $\U_{F_\U} \cong \U$.
%        \item The above 2-equivalence extends to one between 2-categories of arbitrary-base fibrations and arbitrary-domain indexed categories
%        \begin{equation}\label{eq:Gr_equiv}
%        \ICat\simeq\Fib    
%        \end{equation}
    \end{enumerate}
\end{thm}

@@

@@

Under certain conditions, the functor resulting from the Grothendieck construction $p \colon \int{F} \to \mathrm{A}$ will be right adjoint to the desired left adjoint $L \colon \mathrm{A} \to \mathrm{X}$.

{\chris  moved and motivated appropriately}
\begin{thm}\label{thm:mainthmDX}\cite{CV}
Suppose that $\D$ and $\C$ have chosen pushouts and initial objects, and a functor $\U\colon\D\to\C$ strictly preserves them. Then $\U$ is a right adjoint left inverse if and only if $\U$ is an opfibration.
\end{thm}

>>>>

Let $\OpFib(\A)$ denote the 2-subcategory of the slice $\mathbf{Cat}/ \A$ of opfibrations over $\A$, opfibrations morphisms and natural transformations with vertical components. In fact, there is a 2-equivalence between opfibrations over $\A$ and pseudofunctors $\A\to\ca{Cat}$ induced by the so-called Grothendieck construction.

@@

The Grothendieck construction gives rise to a 2-functor $[\A,\mathbf{Cat}] \to \mathbf{Cat}/ \mathrm{A}$ which factors through the image of the embedding $\textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}$ as per the following theorem.
%: $$\int F \colon [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$

\begin{thm}\label{thm:Grothendieck}\hfill
    \begin{enumerate}
        \item Every opfibration $\U \maps \D \to \C$ gives rise to a pseudofunctor $F_U \maps \C {\to}Cat$.
        \item Every opindexed category $F \maps \C \to Cat$ gives rise to  an opfibration $\U_F \colon \int F\to\C$.
        \item The above correspondences yield an equivalence of 2-categories 
        \begin{displaymath}
            ICat(\C) \simeq opFib(\C)
        \end{displaymath}
        so that $F_{\U_F} \cong F$ and $\U_{F_\U} \cong \U$.
%        \item The above 2-equivalence extends to one between 2-categories of arbitrary-base fibrations and arbitrary-domain indexed categories
%        \begin{equation}\label{eq:Gr_equiv}
%        \ICat\simeq\Fib    
%        \end{equation}
    \end{enumerate}
\end{thm}

@@

{\chris A little bit for monoidal Grothendieck here}

For our purposes, we are interested in the fact that under certain conditions, the induced monoidal opfibration by the Grothendieck construction $ \int{F} \to \A$ will be a right adjoint to some adjoint $L_F \colon \A \to \X$, and moreover the unit of the adjunction is the identity; this is called \emph{lari} in [Gray].

{\chris in progress, probably split up in two}
\begin{thm}\label{thm:mainthmDX}\cite{CV}
Suppose that $\X$ and $\A$ have chosen pushouts and initial objects, and a functor $\U\colon\X\to\A$ strictly preserves them. Then $\U$ is a right adjoint left inverse if and only if $\U$ is an opfibration.
\end{thm}
